Avoiding tipping points in ecosystem based fisheries management: a non-parametric Bayesian approach

### 2014-05-14 manuscripts/manuscript.Rmd
re-wrap some text
fix equation reference

We consider three candidate parametric models of the stock-recruitment
dynamics: The Ricker model, the Allen model [@Allen2005], the Myers
model [@Myers1995], equations~\ref{ricker}-\ref{myers}, which we parameterize as follows:

@@

<!-- FIXME ... say much more about the GP, as per Munch 2005a   -->
<!-- See much longer discusion above on "Background on GP".  Move some of that to here?  -->

@@

<!--
In contrast to the parametric models, this posterior distribution is still
conditional on the training data. As such, the uncertainty near the
observed data.
-->

@@

```{r figure_7, fig.height=6, dependson=c("sensitivity-calc", "export-data"), fig.cap="Sensitivity Analysis.  Histogram shows the ratio of the realized net present value / profits derived when managing under the GPDP Gaussian process approach over the optimal value given the true model and true parameters. Values near 1 indicate nearly optimal performance. Simulations cover a range of underlying parameter, model, replicate, and noise levels.", echo=TRUE}
ggplot(sensitivity_dat) + 
  geom_histogram(aes(value, fill=noise)) + 
  xlim(0,1.0) + 
  theme_bw() + 
  xlab("value as fraction of the optimal") + 
  facet_wrap(~model, ncol=1)
```

>>>>

We consider three candidate parametric models of the stock-recruitment
dynamics: The Ricker model, the Allen model [@Allen2005], the Myers
model [@Myers1995], equations (@ricker)-(@myers), which we parameterize as follows:

@@

@@

@@

```{r figure_7, fig.height=6, dependson=c("sensitivity-calc", "export-data"), fig.cap="Sensitivity Analysis.  Histogram shows the ratio of the realized net present value / profits derived when managing under the GPDP Gaussian process approach over the optimal value given the true model and true parameters. Values near 1 indicate nearly optimal performance. Simulations cover a range of underlying parameter, model, replicate, and noise levels."}
ggplot(sensitivity_dat) + 
  geom_histogram(aes(value, fill=noise)) + 
  xlim(0,1.0) + 
  theme_bw() + 
  xlab("value as fraction of the optimal") + 
  facet_wrap(~model, ncol=1)
```
